Age-related changes in plant growth and traits

### 2015-12-23 Accessory_figs_2015_12.Rmd
additional plots, stats tests looking at how different components of accessory costs shift with seed size, age
confirming that calculations based on Lord's papers match those I did earlier

>>>>

SummaryInd$check <- SummaryInd$prepollen_all_inv / (SummaryInd$count_aborted + SummaryInd$seed_count)

plot(check ~ prepollencosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
abline(0,1)

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
options(scipen = 999)

plot(seedcosts ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seedcosts),data=subset(SummaryInd, seedcosts>0))
words.bottom.right.logxy(mod)

plot(prepollencosts ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(prepollencosts),data=subset(SummaryInd,prepollencosts>0))
words.bottom.right.logxy(mod)

plot(abortedcosts ~ seed_size,data=subset(SummaryInd, abortedcosts>.001),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(abortedcosts),data=subset(SummaryInd, abortedcosts>0.001))
words.bottom.right.logxy(mod)

plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",ylab="per seed cost to procur pollen")
mod <- lm(log(seed_size) ~ log(b_div_p),data=subset(SummaryInd,b_div_p>0))
words.bottom.right.logxy(mod)

plot(c_div_p ~ seed_size,data=subset(SummaryInd,c_div_p>0&species!="COER"),col=col.spp(species),pch=16,log="xy",ylab="per seed cost of aborted fruits and seeds")
mod <- lm(log(seed_size) ~ log(c_div_p),data=subset(SummaryInd,c_div_p>0&species!="COER"))
words.bottom.right.logxy(mod)

plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",ylab="cost of dispersal tissues")
mod <- lm(log(seed_size) ~ log(dispersalcosts_increment),data=subset(SummaryInd))
words.bottom.right.logxy(mod)

plot(total_accessory_Lord ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="total per seed accessory costs")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
summary(mod)
```

```{r}
plot(b_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
mod <- lm(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0),slope.test=1)
summary(slopes)

plot(c_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]],c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
mod <- lm(log(c_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,c_div_p>0.00001))
words.bottom.right.logxy(mod)
summary(mod)
slopes <- sma(log(c_div_p) ~ log(seed_size),data=subset(SummaryInd,c_div_p>0),slope.test=1)
summary(slopes)

plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy", ylab="per seed cost of packaging and disp")
mod <- lm(log(dispersalcosts_increment) ~ log(seed_size)*age,data=subset(SummaryInd,dispersalcosts_increment>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(dispersalcosts_increment) ~ log(seed_size),data=subset(SummaryInd,dispersalcosts_increment>0),slope.test=1)
summary(slopes)

plot(total_accessory_Lord  ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
summary(slopes)

#calculation of total accessory investment divided by seed count (accessory_per_seed) very closely correlated with accessory costs per seed using the equations in Lord
plot(total_accessory_Lord  ~ accessory_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
summary(slopes)
summary(mod)

plot(seed_to_ovule_ratio ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seed_size) ~ log(seed_to_ovule_ratio),data=subset(SummaryInd,seed_to_ovule_ratio>0))
words.bottom.left.logxy(mod)

#on an energy basis, propagule inv and accessory inv increase 1 to 1; implies seed size is sufficient information, but need to account of additional component
plot(accessory_inv ~ propagule_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(propagule_inv) ~ log(accessory_inv)*age,data=subset(SummaryInd,propagule_inv>0))
words.bottom.right.logxy(mod)
slopes <- sma(log(propagule_inv) ~ log(accessory_inv),data=subset(SummaryInd,propagule_inv>0),slope.test=1)
summary(slopes)
```
